Open Data

### 2020-06-11 draft_chapter.Rmd
anon & Word version

---
title: "Open Data"
author: "Samuel Langton (MMU) & Reka Solymosi (University of Manchester)"
date: "June 2020"
output:
  pdf_document:
    latex_engine: xelatex
editor_options: 
  chunk_output_type: console
bibliography: refs.bib
---

@@

```{r crimeload_gh, eval = FALSE}
btp_df <- read_csv("https://raw.githubusercontent.com/langtonhugh/osm_crim/master/data/
                   2019-01-greater-manchester-street.csv")
```

>>>>

---
title: "Open Data"
date: "June 2020"
editor_options:
  chunk_output_type: console
output:
  word_document: default
  pdf_document:
    latex_engine: xelatex
bibliography: refs.bib
---

@@

```{r crimeload_gh, eval = FALSE}
btp_df <- read_csv("https://raw.githubusercontent.com/anonymous/osm_crim/master/data/
                   2019-01-greater-manchester-street.csv")
```
